Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, and the WEAI Conference}

### 2023-02-27 latex/paper/Spillover.tex
Rework paper to make it more concise and fix some proofs

\title{Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Brantly Callaway, Pedro Sant'Anna, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, the Urban Economics Association Conference, the WEAI Conference, and the University of Rochester HEEL Lab for helpful comments.}}
\author{\href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado Boulder, Economics Department (\href{mailto:kyle.butts@colorado.edu}{kyle.butts@colorado.edu})}}
\date{\today}

@@

@@

    \begin{abstract}
        {\small
        Empirical work often uses treatment assigned following geographic boundaries. When the effects of treatment cross over borders, classical difference-in-differences estimation produces biased estimates for the average treatment effect. In this paper, I introduce a potential outcomes framework to model spillover effects and decompose the estimate's bias in two parts: (1) the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment and (2) changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. I propose estimation strategies that can remove both sources of bias and semi-parametrically estimate the spillover effects themselves including in settings with staggered treatment timing. To highlight the importance of spillover effects, I revisit analyses of three place-based interventions.

@@

Empirical work in economics often considers settings where a policy is targeted to groups of units defined by geographic boundaries, but the effect of treatment spills over onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g. geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, individuals in control areas can travel to the treated areas and receive treatment (e.g. a hospital opening serves nearby residents), or shocks to a labor market can affect nearby areas (e.g. a new factory opening increases service sector spending in the entire commuting zone). For other treated units, the treatment effect can depend on other units' treatment status. Forces of agglomeration can increase effect size as treatment concentration increases (e.g. knowledge-sharing between firms) or forces of congestion/competition can decrease the effects of treatment (e.g. bidding up of wages causes the employment effects of factory openings to be mitigated).

In this paper, I introduce a potential outcomes framework that directly models spillover effects and use this model to derive identification results in difference-in-differences settings. Using this potential outcome framework, I define different possible treatment effects of interest, discuss their interpretation, and show which effects are non-parametrically identified.

First, there is the `switching effect' which is the relevant parameter for local policymakers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''. It is difficult to estimate the switching effect without parametric assumptions on spillovers. The reason for this is that the magnitude of the switching effect potentially depends on the treatment status of a unit's neighbors. For example, the construction of low-cost medical facilities will have larger treatment effects when neighboring areas do not have facilities. Switching effects therefore are defined separately for each level of exposure and estimation of the effect at a particular level requires knowledge of which control units experience the same level of exposure. I show that identification therefore requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the homogeneity of spillover effects. While the switching effect is not identified nonparametrically in general, the switching effect for units with zero exposure is identified under mild assumptions. I call this effect the `direct effect' which measures the effects of turning on a unit's treatment if they were the \emph{only} unit to be treated in their general area.

The second effect of interest is the `total effect' which is the relevant parameter for national policymakers who want to answer ``What is the average effect of implementing the entire treatment regime?''. This treatment effect summarizes the post-hoc effects of going from the world with no treatment to the observed treatment vector. This effect comes from two sources: the direct effect on each treated unit and the average spillover effect on to treated units from other treated units.

This paper then defines conditions under which the direct and total effects are nonparametrically identified by a modified difference-in-differences type estimand under a mild assumption that spillovers are `local' in nature. The local spillovers assumption holds in the case where spillover effects are only experienced by units within a certain distance of treated units. This would hold in the case where individuals can travel to access treatment and therefore spillovers are limited by travel costs. However, this would fail in the case of large general equilibrium shocks that cause units far away to be affected by treatment (e.g. San Francisco being affected by shocks to the New York economy).

Next, I assess the commonly used difference-in-differences estimate. This paper shows that the difference-in-differences estimator is a biased estimate for the direct and the total effect. This bias arises because untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend. Difference-in-differences estimates average the spillover onto the `close' control units into the untreated units' change in outcomes. Hence, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect. For example, if nearby control units also benefit from treatment, then researchers would underestimate the treatment effect of the treated. The direct effect also has a second source of bias because changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of `close' units. In difference-in-differences, the spillover onto other treated units is averaged into the treated units' change in outcomes. Therefore the bias on the direct effect estimate is the same sign as the sign of the spillover.

Under the assumption that spillovers are local, I formalize the identification argument used in a common adjustment of including an indicator for being affected by spillovers (or removing them from the sample) in the two-way fixed-effects model. I show, under mild assumptions, that this method will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers. The bias term in the difference-in-differences estimate for the total effect is the \textit{average} spillover effects onto control units. An indicator variable that contains \emph{all} control units affected by spillover can therefore remove this bias. However, adding this indicator changes the underlying control group to the control units not included in the indicator variable and hence a researcher must justify why this subsample will form a valid control group for the parallel trends assumption. When estimating the direct effect, a second indicator variable containing \emph{all} treated units affected by spillovers can remove the second source of bias. Similar to the control group indicator, this modifies the treatment group over which the average treatment group is taken (those with indicator equal to zero). Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space. The primary assumption required is selecting the maximum distance from treated units that spillovers can occur.\footnote{Since treatment effects typically decay over distance, this is not a strong assumption. Even if the maximum distance is not large enough, most of the bias will still be removed. On the other hand, making the maximum distance too large will increase the variance in the estimates as there are fewer remaining control units to identify the parallel counterfactual unit.}

The modified difference-in-differences framework with an added spillover indicator provides a poor estimate of spillover effects. The estimate averages spillover effects over all units with the indicator equal to 1 which can include units that are unaffected by spillovers. Therefore the estimate will be attenuated to zero. The above method can be improved by creating a set of distance bins from the treated units (e.g. being 0-20 miles, 20-40 miles, 40-60 miles from the treated units) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers. In some cases, the bins can be determined in a data-driven way \citep{Butts_2021}.} Since a set of `rings' is collinear with a single indicator covering the bins, this estimator consistently estimates the treatment effect of interest. This estimator has the added benefit that each indicator will estimate the average spillover effect on treated/control units within that distance range which provides a more complete picture of which units are affected by treatment and at what magnitude.

@@

Last, in Section \ref{sec:event_study}, I extend estimation of the direct effect and spillover effects of treatment into the TWFE/event-study framework by extending the work of \citet{Gardner_2021}. This allows for a very common setting in which treatment turns on for different units in different periods. Their proposed two-stage estimator first estimates group and time fixed-effects using untreated/not-yet-treated observations. Since some control/not-yet-treated units can be affected by spillovers, these units must be removed to consistently estimate the group and time fixed-effects. Then these estimated unit and time fixed-effects are subtracted from the observed outcome \emph{in the full sample}. The resulting residuals are then regressed on the treatment and spillover variables to estimate treatment and spillover effects. In the online appendix, I demonstrate the method by revisiting the analysis by \citet{Bailey_Goodman_Bacon_2015} of Community Health Centers which provided low-cost primary care to impoverished areas.

@@

I contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework in three ways \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}. My paper is the first to consider identification in terms of general potential outcomes. Other papers derive results for specific spillover mappings. If I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs. The literature has focused on estimating the total effect, so I further contribute by discussing alternative treatment effect estimates and identification results. Last, my paper also advances the literature by considering estimation of direct effects and spillover effects in the event-study framework which allows for the common occurrence of staggered treatment adoption.

This paper relates to a broad literature on spillover effect estimation in randomized experiments.\footnote{See \citet{Sobel_2006} and \citet{Hudgens_Halloran_2008} for early work. See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{Vazquez-Bare_2019} and references therein for recent work on this.} There are two main strands of this literature. First, there is a large literature on the estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers. Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemiology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares units in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects. This allows standard difference-in-differences estimation of both the total effect (treatment effect on the treated) and spillover effects (treatment effect on the untreated in the treated clusters). However, in many settings distinct clusters are not plausible, e.g. counties near the border of a state can affect each other. My proposed estimator generalizes this method by using control units that are unaffected by treatment without requiring a notion of clusters.

There is also a nascent literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster in experimental settings (\citet{Savje_Aronow_Hudgens_2021}, \citet{Vazquez-Bare_2019}, and \citet{Hu_Li_Wager_2021}). Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, including a modified parallel-trends assumption, for identification in non-experimental settings. I contribute to this literature by formalizing identification results of different treatment effects in non-experimental settings.

The rest of the paper is structured as follows. Section \ref{sec:po_framework} presents the potential outcomes framework, defines the estimand of interest, discusses identification of effects, and shows the resulting bias from estimating a classical difference-in-differences model. Section \ref{sec:estimation} focuses on the estimation of the direct effect, the total effect, and spillover effects. Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program. Last, Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Gardner_2021} and \citet{Borusyak_Jaravel_Spiess_2021}.

@@

\begin{assumption}[Random Sampling]\label{assumption:random}
    $\{ Y_{i0}, Y_{i1}, D_{i} \}_{i = 1}^{n}$ is an independent and identically distributed sample of panel data.
\end{assumption}

Assumption (\ref{assumption:random}) allows me to consider observations as coming from a larger population (sometimes called a superpopulation). Later, when discussing inference, I will relax this assumption to account for spatial correlation between observations, but identification does not rely on independence. As an alternative, inference could come from a design-based perspective following \citet{Athey_Imbens_2021}.

Potential outcomes, denoted $Y_{it}(D_i, h_i(\vec{D}))$, are a function of unit $i$'s own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments. The non-negative scalar- or vector-valued function $h_i(\vec{D})$ is referred to as an `exposure mapping'. This setup follows \citet{Vazquez-Bare_2019} who studies identification of spillover effects under an experimental setting.\footnote{Note that throughout, expectations and inference are conditional on the vector of exposure mappings. In design-based settings, the distribution of exposure mappings is known so expectations can be taken without conditioning on the vector of exposure mappings. See \citet{Savje_Aronow_Hudgens_2021} for discussion estimation and inference when the treatment design is known.}

The exposure mapping formalizes violations to the stable-unit treatment value assumption (SUTVA) by summarizing the intensity at which unit $i$ is affected by spillovers. Without any restrictions on the exposure mapping, nonparametric identification of treatment effects is impossible. The main assumption for identification, as is formalized in section \ref{sec:remove_bias}, is that when unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h_i(\vec{D}) = \vec{0}$ . In the world of no spillovers, that is $h_i(\vec{D}) = \vec{0}$ for all individuals, potential outcomes would return to only depending on own-treatment status.

The identification results of this paper do not require parameterization of the exposure mapping. However, to help better understand the exposure mapping, I give three examples that are commonly used in the literature.

\begin{example}
    $h_i(\vec{D})$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly, a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure that is the distance between unit $i$ and $j$.  In this case \begin{equation}\label{eq:h_within}
        h_i(\vec{D}) = \max_{j \neq i} D_j * \one_{ d(i,j) < \bar{d}}
    \end{equation}
    This exposure mapping is a realistic specification when it is assumed that spillover effects do not decay over distance until $\bar{d}$ and the intensity of spillovers does not depend on the number of neighboring units treated. For example, this exposure mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}. In this case, the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library. The benefits of access to a neighboring town library do not depend on whether people can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.  
\end{example}

\begin{example}
    Second, $h_i(\vec{D})$ can be a function that equals the number of units treated within distance $\bar{d}$, i.e. \begin{equation}\label{eq:h_within_additive}
        h_i(\vec{D}) = \sum_{j \neq i} D_j * \one_{d(i,j) < \bar{d}}.
    \end{equation}
    This exposure mapping is no longer binary, so the intensity of spillovers is additive in the number of nearby units treated. In the context of wholesale store openings, this exposure mapping captures the additive nature of agglomeration economies. As more nearby counties receive new stores, the force of agglomeration and therefore the spillover effect increases (e.g. \citet{Basker_2005}).
\end{example}

\begin{example}
    Last, $h_i(\vec{D})$ is a spatial decay function where exposure decreases with distance. In this case, spillover intensity is the sum across all treated observations' decay terms, i.e. \begin{equation}\label{eq:h_decay}
        h_i(\vec{D}) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
    \end{equation} 
    This exposure mapping allows for the intensity of spillovers to depend on the distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units. This creates problems with inference because it implies a potential correlation between all units' error terms. For this reason, this function often is summed over only the $k$-nearest neighbors or units within $\bar{d}$ miles.} The speed that spillover effects decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using a non-linear least-squares routine. In the literature on R\&D investment, for example, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure. This specification features exponential decay over distance which captures the theoretical insight that research spending in closer locations has a larger effect than further away spending.
\end{example}

Often, researchers will try to parameterize potential outcomes by reasoning through the nature of the spillovers in a way similar to the above examples. Estimation in this case will rely on the functional form assumptions made by researchers. This paper will take an alternative approach to identification and estimation which will allow for estimation of treatment effects without requiring direct knowledge of the functional form of the exposure mapping/potential outcomes.

In particular, I will redefine the standard difference-in-differences identifying assumptions in the context of the new potential outcome framework. First, I assume that units do not adjust their actions in period $0$ from knowledge of future treatment:
\begin{assumption}[No Anticipation]\label{assumption:no-anticipation}
    $Y_{i0}(D, h) = Y_{i0}(0,0)$ for all values of $D$ and $h$.
\end{assumption}
Second, I formalize the parallel counterfactual trends assumption as follows:
\begin{assumption}[Parallel Counterfactual Trends]\label{assumption:parallel}
    Counterfactual trends do not depend on $D_i$:
    \[ 
        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1 } = 
        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0 }
    \]
\end{assumption}
This assumption states that in the absence of treatment and with zero exposure (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status. This generalizes to the classic parallel counterfactual trends when SUTVA is satisfied because then every unit has zero exposure.

@@

% Work by \citet{Savje_Aronow_Hudgens_2021} suggests averaging the switching effect over exposure levels,
%\[ 
%    \tau_{\text{avg,switch}} \equiv \expec{\tau_{i, switch}(h_i(\vec{D})) \vert D_i = 1}.
%\] 
%This estimand averages the switching effect over all treated units and hence average over the distribution of exposure. Any given unit $i$ trying to understand the effect of switching on a policy can't use this parameter as it averages over exposures different than theirs. More, this parameter can not be identified without further assumptions as the distribution of exposure mappings is not necessarily the same for control units as treated units.\footnote{\citet{Savje_Aronow_Hudgens_2021} discuss conditions on the distribution of exposure mappings that can lead to asymptotic identification of the average switching effect. However it relies on design-based assumptions that do not apply here.}

There is a particular switching effect at zero exposure that I call the `direct effect' of treatment, 
\[
    \tau_{\text{direct}} \equiv \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, h_i(\vec{D}) = \vec{0}} = \tau_{\text{switch}}(\vec{0}),
\] 
which measures the average effect of being treated \emph{among unexposed treated units}. Specifying this particular switching effect will prove useful when discussing identification as it requires fewer assumptions than switching effects at other exposure levels. As discussed above, this is not necessarily a policy-relevant parameter for every unit if the switching effect has different magnitudes at different levels of exposure.

The second policy-relevant parameter is the `total effect of treatment': 
\[
    \tau_{\text{total}} \equiv \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1}.
\] 
As opposed to the switching effect, which keeps exposure constant, the total effect looks at turning on treatment \emph{and} going from zero exposure to $h_i(\vec{D})$ simultaneously. This can be thought of as going from the world with a \emph{complete} absence of treatment, $\vec{0}$ to the current treatment vector $\vec{D}$. This treatment effect is helpful for `national' policymakers to evaluate what \emph{were} the effects of the entire vector of \emph{enacted policies}.

@@

This assumption requires parallel trends among treated and control units at exposure $\vec{h}$. This assumption is implied by \nameref{assumption:parallel} and an additional assumption that spillover effects are equal between control and treated units that experience exposure $\vec{h}$. Under this assumption, the switching effect can be identified.

@@

\subsubsection{Direct and Total Effects}

>>>>

\title{Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Brantly Callaway, Pedro H.C. Sant'Anna, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, the Urban Economics Association Conference, the WEAI Conference, and the University of Rochester HEEL Lab for helpful comments.}}
\author{\href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado Boulder, Economics Department (\href{mailto:kyle.butts@colorado.edu}{kyle.butts@colorado.edu})}}
\date{\today}

@@

% Conditionally display thoughts
% https://tex.stackexchange.com/questions/33576/conditional-typesetting-build
\usepackage{etoolbox}

\newtoggle{INCLUDECOMMENTS}
\toggletrue{INCLUDECOMMENTS}
% \togglefalse{INCLUDECOMMENTS}

\newcommand{\nick}[1]{\iftoggle{INCLUDECOMMENTS}{{\color{cranberry}\textbf{Nick:} #1}}{}}
\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{{\color{cranberry}\textbf{Kyle:} #1}}{}}

@@

    \begin{abstract}
        {\small
        Empirical work often uses treatment assigned following geographic boundaries. When the effects of treatment cross over borders, classical difference-in-differences estimation produces biased estimates for the average treatment effect. In this paper, I introduce a potential outcomes framework to model spillover effects and decompose the estimate's bias in two parts: (1) the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment and (2) changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. I propose conditions for non-parametric identification that can remove both sources of bias and semi-parametrically estimate the spillover effects themselves including in settings with staggered treatment timing. To highlight the importance of spillover effects, I revisit analyses of three place-based interventions.

@@

Empirical work in economics often considers settings where a policy is targeted to groups of units defined by geographic boundaries, but the effect of treatment spills over onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g. geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, individuals in control areas can travel to the treated areas and receive treatment (e.g. a hospital opening serves nearby residents), or shocks to a labor market can affect nearby areas (e.g. a new factory opening increases service sector spending in the entire commuting zone). In some cases, the treatment effect may depend on the treatment status of other units. The concentration of treatment can increase its impact through knowledge-sharing between firms, while congestion or competition may decrease its effects, such as when wage bids mitigate employment effects of factory openings.

Estimation of treatment effects in these settings typically proceed in two ways. One approach involves using a structural model to account for general equilibrium effects. For example, trade models generate a market access term that effectively controls for such effects \citep{Donaldson_Hornbeck_2016} or the common Manski linear-in-means model controls for the average characteristics of a unit's peers \citep{manski1993identification,goldsmith2013social}. Another strategy involves excluding units located close to the treatment area (or including a dummy variable) to avoid any spillover biases on the effects, which is preferred by researchers who wish to remain agnostic to structural assumptions. This paper adopts the latter non-parametric approach and formalizes the identification assumptions required to interpret the estimates causally.

To do so, this paper introduces a potential outcomes framework following \citet{vazquez2022identification} and extends the framework to difference-in-differences settings. Since potential outcomes are now characterized by a unit's treatment status as well as the treatment status of other units, there are many potential treatment effects that can be formualted. I study two relevant treatment effects. The second effect of interest is the `total effect' which is the relevant parameter for national policymakers who want to answer ``What is the average effect of implementing the entire treatment regime?''. This treatment effect summarizes the post-hoc effects of going from the world with no treatment to the observed treatment vector. First, there is the `switching effect' which is the relevant parameter for local policymakers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''.

After defining these effects, I discuss non-parametric identification results extending standard parallel-trends assumptions to settings with spillovers. First, I demonstrate that the `total effect' can be identified under assumptions that spillovers are ``local'' and only affect nearby units, while parallel trends exist between treated and non-affected ``far-away'' units. This would hold in the case where individuals can travel to access treatment and therefore spillovers are limited by travel costs. However, this assumption may not hold in the case of large general equilibrium shocks that affect units far away from the treatment area, such as when New York's economy impacts San Francisco.

Estimating the switching effect without parametric assumptions on spillovers is challenging since the effect's magnitude often depends on the treatment status of neighboring units. For instance, the construction of low-cost medical facilities will have more substantial treatment effects when neighboring areas lack such facilities. As a result, switching effects must be defined separately for each level of exposure, and estimating the effect at a specific level necessitates knowledge of which control units share the same level of exposure. I demonstrate that identification requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the homogeneity of spillover effects.

Subsequently, the commonly used difference-in-differences estimator is evaluated. The study demonstrates that this estimator produces biased estimates for both the total effects. This bias arises from the fact that untreated units that are "close" to treated units experience treatment effects, thereby failing to identify the counterfactual trend. The difference-in-differences estimate averages the spillover onto the "close" control units into the untreated units' change in outcomes. As a result, the spillover is subtracted from the estimated treatment effect, introducing bias in the opposite sign of the spillover effect.

Then, I formalize the identification strategy commonly used to adjust for spillovers by including an indicator variable for units affected by spillovers (or removing them from the sample) in the two-way fixed-effects model. I show, under mild assumptions, that this method will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers. However, adding this indicator changes the underlying control group to the control units not included in the indicator variable and hence a researcher must justify why this subsample will form a valid control group for the parallel trends assumption. Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space. The primary assumption required is selecting the maximum distance from treated units that spillovers can occur.\footnote{Since treatment effects typically decay over distance, this is not a strong assumption. Even if the maximum distance is not large enough, most of the bias will still be removed. On the other hand, making the maximum distance too large will increase the variance in the estimates as there are fewer remaining control units to identify the parallel counterfactual unit.}

The modified difference-in-differences framework with an added spillover indicator provides a poor estimate of spillover effects. The estimate averages spillover effects over all units with the indicator equal to 1 which can include units that are unaffected by spillovers. Therefore the estimate will be attenuated to zero. The above method can be improved by creating a set of distance bins from the treated units (e.g. being 0-20 miles, 20-40 miles, 40-60 miles from the treated units) and interacting them with a treatment indicator. Since a set of `rings' is collinear with a single indicator covering the bins, this estimator consistently estimates the treatment effect of interest. This estimator has the added benefit that each indicator will estimate the average spillover effect on treated/control units within that distance range which provides a more complete picture of which units are affected by treatment and at what magnitude. However, interpreting these estimates causally requires that each ring satisfies a parallel trends assumption with the `far-away' control units.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers. In some cases, the bins can be determined in a data-driven way \citep{Butts_2021}.}

@@

Last, in Section \ref{sec:event_study}, I extend estimation of treatment and spillover effects into the TWFE/event-study framework by extending the work of \citet{Gardner_2021}. This allows for a very common setting in which treatment turns on for different units in different periods. Their proposed two-stage estimator first estimates group and time fixed-effects using untreated/not-yet-treated observations. Since some control/not-yet-treated units can be affected by spillovers, these units must be removed to consistently estimate the group and time fixed-effects. Then these estimated unit and time fixed-effects are subtracted from the observed outcome \emph{in the full sample}. The resulting residuals are then regressed on the treatment and spillover variables to estimate treatment and spillover effects. In the online appendix, I demonstrate the method by revisiting the analysis by \citet{Bailey_Goodman_Bacon_2015} of Community Health Centers which provided low-cost primary care to impoverished areas.

@@

I contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework in three ways \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}. My paper is the first to consider non-parametric identification in terms of general potential outcomes. Other papers derive results for specific spillover mappings. If I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs. The literature has focused on estimating the total effect, so I further contribute by discussing alternative treatment effect estimates and identification results. Last, my paper also advances the literature by considering estimation of treatment effects and spillover effects in the event-study framework which allows for the common occurrence of staggered treatment adoption.

This paper relates to a broad literature on spillover effect estimation in randomized experiments.\footnote{See \citet{Sobel_2006} and \citet{Hudgens_Halloran_2008} for early work. See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{vazquez2022identification} and references therein for recent work on this.} There are two main strands of this literature. First, there is a large literature on the estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers. Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemiology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares units in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects. This allows standard difference-in-differences estimation of both the total effect (treatment effect on the treated) and spillover effects (treatment effect on the untreated in the treated clusters). However, in many settings distinct clusters are not plausible, e.g. counties near the border of a state can affect each other. My proposed estimator generalizes this method by using control units that are unaffected by treatment without requiring a notion of clusters.

There is also a nascent literature exploring estimation of treatment and spillover effects which does not require a completely untreated cluster in experimental settings (\citet{Savje_Aronow_Hudgens_2021}; \citet{vazquez2022identification}; \citet{Hu_Li_Wager_2021}; \citet{yu2022estimating}). Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, based on a modified parallel-trends assumption, for identification in non-experimental settings. I contribute to this literature by formalizing identification results of different treatment effects in non-experimental settings.

The rest of the paper is structured as follows. Section \ref{sec:po_framework} presents the potential outcomes framework, defines the estimand of interest, discusses identification of effects, and shows the resulting bias from estimating a classical difference-in-differences model. Section \ref{sec:estimation} focuses on the estimation of the total effect and spillover effects. Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program. Last, Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Gardner_2021} and \citet{Borusyak_Jaravel_Spiess_2021}.

@@

Potential outcomes, denoted $Y_{it}(D_i, h_i(\vec{D}))$, are a function of unit $i$'s own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments. The non-negative scalar- or vector-valued function $h_i(\vec{D})$ is referred to as an `exposure mapping'. This setup follows \citet{vazquez2022identification} who studies identification of spillover effects under an experimental setting. Assumption (\ref{assumption:random}) allows me to consider observations as coming from a larger population (sometimes called a superpopulation).\footnote{Note that throughout, expectations and inference are conditional on the treatment vector (and hence exposure mappings) as in \citet{Borusyak_Jaravel_Spiess_2021}. In design-based settings, the distribution of exposure mappings is known so expectations can be taken without conditioning on the vector of exposure mappings. See \citet{Savje_Aronow_Hudgens_2021} for discussion estimation and inference when the treatment design is known.}

\begin{assumption}[Random Sampling]\label{assumption:random}
  $\{ Y_{i0}, Y_{i1} \}_{i = 1}^{n}$ is an independent and identically distributed sample of panel data.
\end{assumption}

The exposure mapping formalizes violations to the stable-unit treatment value assumption (SUTVA) by summarizing the intensity at which unit $i$ is affected by spillovers. Without any restrictions on the exposure mapping, nonparametric identification of treatment effects is impossible. The main assumption for identification, as is formalized in section \ref{sec:remove_bias}, is that when unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h_i(\vec{D}) = \vec{0}$ . In the world of no spillovers, that is $h_i(\vec{D}) = \vec{0}$ for all individuals, potential outcomes would return to only depending on own-treatment status.\footnote{For example, $h_i(\vec{D})$ could be an indicator for being within a certain distance of a treated unit. Additionally, exposure could be defined as a spatial decay function where exposure is declining in the distance of treated units.}

Often, researchers will try to parameterize potential outcomes by reasoning through the nature of the spillovers and subsequent estimation will rely on the functional form assumptions made by researchers. This paper will take an alternative approach to identification and estimation which will allow for estimation of treatment effects without requiring direct knowledge of the functional form of the exposure mapping/potential outcomes.

In particular, I will redefine the standard difference-in-differences identifying assumptions in the context of the new potential outcome framework. First, I assume that units do not adjust their actions in period $0$ from knowledge of future treatment:
\begin{assumption}[No Anticipation]\label{assumption:no-anticipation}
    $Y_{i0}(D, h) = Y_{i0}(0,0)$ for all values of $D$ and $h$.
\end{assumption}
Second, I formalize the parallel counterfactual trends assumption as follows:
\begin{assumption}[Parallel Counterfactual Trends]\label{assumption:parallel}
    Counterfactual trends do not depend on $D_i$:
    \[ 
        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1 } = 
        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0 }
    \]
\end{assumption}
This assumption states that in the absence of treatment and with zero exposure (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 do not depend on treatment status. This generalizes to the classic parallel counterfactual trends when SUTVA is satisfied because then every unit has zero exposure.

@@

The second policy-relevant parameter is the `total effect of treatment on the treated': 
\[
    \tau_{\text{total}} \equiv \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1}.
\] 
As opposed to the switching effect, which keeps exposure constant, the total effect looks at turning on treatment \emph{and} going from zero exposure to $h_i(\vec{D})$ simultaneously. This can be thought of as going from the world with a \emph{complete} absence of treatment, $\vec{0}$ to the current treatment vector $\vec{D}$. This treatment effect is helpful for `national' policymakers to evaluate what \emph{were} the effects of the entire vector of \emph{enacted policies}.\footnote{\citet{yu2022estimating} label the `total effect' to be $\expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0})}$ where the average is over all units including control units. Identification of this effect relies on assumptions about experimental-design so this paper does not pursuit identification of this effect.}

@@

This assumption requires parallel trends among treated and control units at exposure $\vec{h}$. Under this assumption, the switching effect can be identified by a difference-in-differences estimand calculated using only units with an exposure of $\vec{h}$.

@@

\subsubsection{Total Effect}

To identify the total effect, additional assumptions on the nature of spillover effects are needed. In particular, I will formalize the idea that spillovers are `local' in that units are only affected by treatment if they are near treatment. For example, if treatment has to be accessed in person, then it is natural that further away places are not affected by treatment. However, this assumption may fail under general equilibrium shocks that do not necessarily decay over distance.
